\documentclass[10pt,letterpaper]{article}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\begin{document}

1.	Find the point of intersection of $2x + y = 5$ and $x - 3y = 7$.

2.	Use distances to determine whether or not the three points $(1, 5)$, $(-2, -1)$ and $(4, 10)$ are collinear. Check your work by using slopes.

3.	Find the lengths of the medians of the triangle with vertices $(-3, 4)$, $(5, 5)$ and $(3, -2)$.

4.	Use distances to determine whether or not the points $(1, 6)$, $(5, 3)$ and $(3, 1)$ are the vertices of a right triangle. Check your work by using slopes

5.	Determine $x$ so that $(x, 1)$ is on the line joining $(0, 4)$ and $(4, -2)$.

6.	Line $l_1$ contains the points $(4, 7)$ and $(2, 3)$, while $l_2$ contains $(5, 6)$ and $(-3, 4)$. Are $l_1$ and $l_2$ parallel, perpendicular, coincident, or none of these?

7.	Find the slopes of the altitudes of the triangle with vertices (-2, 4), (3, 3), and (-5 , -2).

8.	Find the points of trisection of the segment joining (2, -5) and (-3, 7).

9.	Find an equation of the perpendicular bisector of the segment joining (5, -3) and (-1, 1).
\begin{quote}
[Hint: What is the relationship between a point on the desired line and the two given points?]"
\end{quote}

10.	Find the points of intersection of $x - 7y + 2 = 0$ and $x^2 + y^2 - 4x + 6y - 12 = 0$. Sketch it.

11.	The point $(5, -2)$ is at a distance $\sqrt{13}$ from the midpoint of the segment joining $(5, y)$ and $(-1, 1)$. Find $y$.

12.	Prove analytically that the lines joining the middpoints of adjacent sides of a quadilateral form a parallelogram.

13.	Find the point of intersection of the medians of the triangle with vertices $(4, -3)$, $(-2, 1)$, and $(0, 5)$. (See Problem 26, page 16.)

14.	Find an equation for the set of all points (x, y) such that it is equidistant from $(0, 1)$ and the $x axis$.

15.	Find the center of the circle circumscribed about the triangle with vertices $(-1, 1)$, $(6, 2)$, and $(7, -5)$.

16.	Two vertices of an equilateral triangle are $(a, -a)$ and $(-a, a)$. Find the third.

17.	A square has all its vertices in the first quadrant and one of its sides $(3, 1)$ and $(6, 3)$. Find the other two vertices.

18.	A parallelogram has three vertices $(3, 4)$, $(6,3)$, and $(1, 0)$ and the fourth vertex in the first quadrant. Find the fourth vertex.

19.	Find an equation for the set of all points $(x, y)$ such that the angle from the $x$ axis to the line joining $(x, y)$ and the origin equals $y$.

\end{document}