\documentclass[10pt,letterpaper]{article}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\begin{document}
\textbf{Analytic Geometry, Third Edition}
\textbf{Section 1.6 - Point-of-Division Formulas}
\newline \textbf{Problems}
\newline \textbf{A}
\newline \textit{In Problems 1-8, find the angle from $l_1$ to $l_2$ with slopes $m_1$ and $m_2$, respectively}
\newline 1. $m_1=-2, m_2=3$
\newline 2. $m_1=1, m_2=4$
\newline 3. $m_1=-3, m_2=2$
\newline 4. $m_1=5, m_2=-1$
\newline 5. $m_1=10, m_2$ does not exist
\newline 6. $m_1=0, m_2=-1$
\newline 7. $m_1=2/3, m_2$ does not exist
\newline 8. $m_1$ does not exist, $m_2=-2$
\\
\newline \textit{In Problems 9-16, find the angle from $l_1$ to $l_2$, where $l_1$ and $l_2$ contain the points indicated}
\newline 9. $l_1:(1,4), (3,-1) l_2:(3,2),(5,-1)$
\newline 10. $l_1:(2,5),(-3,10) l_2:(-1,-3),(3,3)$
\newline 11. $l_1:(4,5),(1,1) l_2:(3,-3),(0,4)$
\newline 12. $l_1:(1,1),(0,5) l_2:(4,3),(-1,2)$
\newline 13. $l_1:(3,4),(3,-1) l_2:(2,5),(-1,2)$
\newline 14. $l_1:(-1,2),(-1,-1) l_2:(-3,4),(1,0)$
\newline 15. $l_1:(5,1),(3,-3) l_2:(5,1),(5,-3)$
\newline 16. $l_1:(3,-4),(2,3) l_2:(2,-3),(2,4)$
\\
\newline \textbf{B}
\newline \textit{In Problems 17-24, find the slope of the line bisecting the angle from $l_1$ to $l_2$ with slope $m_1$ and $m_2$, respectively.}
\newline 17. $m_1=3, m_2=-2$
\newline 18. $m_1=1, m_2=-7$
\newline 19. $m_1=2, m_2=3$
\newline 20. $m_1=-1, m_2=2$
\newline 21. $m_1=-3, m_2=5$
\newline 22. $m_1=2, m_2=0$
\newline 23. $m_1=3/4, m_2$ does not exist
\newline 24. $m_1$ does not exist, $m_2=1$
\newline 25. Find the interior angles of the triangle with vertices $A=(1,5)$, $B=(3,-1$), and $C=(-1,-1$)
\newline 26. Find the interior angles of the triangle with vertices $A=(3,2)$, $B=(4,5)$, and $C=(-1,-1$)
\newline 27. Find the slope of the line $l_1$ such that the angle from $l_1$ to $l_2$ is Arctan 2/3 where $l_2$ contains (2,1) and (-4,-5)
\newline 28. Find the slope of the line $l_1$ such that the angle from $l_1$ to $l_2$ is $45^{\circ}$, where the slope of $l_2$ is -2.
\newline 29. Find the slope of the line $l_2$ such that the tangent of the angle from $l_1$ to $l_2$ is -1/2, where $l_1$ is a vertical line.
\newline 30. A line with slope 1 bisects the angle from $l_1$ to $l_2$, where $l_2$ has slope 2. What is the slope of $l_1$?
\newline 31. A line with slope $3 + \sqrt{10}$ bisects the angle from $l_1$ to $l_2$, where $l_1$ has slope 1. What is the slope of $l_2$?
\newline 32. Show by means of angles that $A=(1,0)$, $B=(4,4)$, and $C=(8,1)$ are the vertices of an isoceles triangle.
\\
\newline \textbf{C}
\newline 33. Lines $l_1$ and $l_2$ have slopes m and 1/m, respectively. What is the slope of the line bisecting the angle from $l_1$ and $l_2$?
\newline 34. If lines $l_1$ and $l_2$ have slopes 1 and m, respectively. What is the slope of the line bisecting the angle from $l_1$ and $l_2$?
\newline \textit{}
\end{document}