\documentclass[10pt,letterpaper]{article}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\begin{document}
\textbf{Analytic Geometry, Third Edition}\\
\textbf{Section 1.4 - Inclination and Slope}\\
\textbf{Section 1.5 - Parallel and Perpendicular Lines}
\newline \textbf{Problems}
\newline \textbf{A} \textit{In Problems 1-8, find the slope (if any) and the inclination of the line through the given points.}
\newline 1. $(2,3),(5,8)$
\newline 2. $(-1,4),(4,2)$
\newline 3. $(-2,-2),(4,2)$
\newline 4. $(3,-5),(1,-1)$
\newline 5. $(-4,2),(-4,5)$
\newline 6. $(2,3),(-4,3)$
\newline 7. $(a,a), (b,b)$
\newline 8. $(a,a), (-a,2a)$
\\
\newline \textit{In Problems 9-14, graph the line through the given point and having the given slope.}
\newline 9. $(5,-2), m=2$
\newline 10. $(-2,4), m=3/4$
\newline 11. $(3,1), m= -1/3$
\newline 12. $(0,4), m=-3$
\newline 13. $(4,2), m=0$
\newline 14. $(-3,1), no slope$
\\
\newline \textit{In Problems 15-22, find the slopes of the lines through the two pairs of points; then determine whether the lines are parallel, coincident, perpendicular, or none of these.}
\newline 15. $(1,-2),(-2,-11); (2,8),(0,2)$
\newline 16. $(1,5),(-2,7); (7,-1),(3,0)$
\newline 17. $(1,5),(-1,-1); (0,3),(2,7)$
\newline 18. $(1,3),(-1,-1); (0,2),(4,-2)$
\newline 19. $(1,1),(4,-1); (-2,3),(7,-3)$
\newline 20. $(1,-4),(6,1); (2,3),(-1,6)$
\newline 21. $(1,2),(3,2); (4,1),(4,-2)$
\newline 22. $(1,5),(1,1); (-2,2),(-2,4)$
\newline 23. Find the pitch (slope) of the roof shown in Figure 1.25.
\\
\newline \textbf{B}
\newline 24. Find the percentage grade of the section of road shown in Figure 1.26
\newline 25. If the line through $(x,5)$ and $(4,3)$ is parallel to a line with slope 3, find $x$.
\newline 26. If the line through $(x,5)$ and $(4,3)$ is perpendicular to a line with slope 3, find $x$.
\newline 27. If the line through $(x,1)$ and $(0,y)$ is coincident with the line through $(1,4)$ and $(2,-3)$, find $x$ and $y$.
\newline 28. If the line through $(-2,4)$ and $(1,y)$ is perpendicular to one through $(-2,4)$ and $(x,2)$.
\newline 29. If the line through $(x,4)$ and $(3,7)$ is parallel to one through $(x,-1)$ and $(5,1)$, find $x$.
\newline 30. Show by means of slopes that $(1,1)$, $(4,1)$, $(3,2)$ and $(0,-2)$, are the vertices of a parallelogram.
\newline 31. Show by means of slopes that $(-2,4)$, $(2,0)$, $(2,8)$, and $(6,4)$ are the vertices of a square.
\newline 32. A certain section of railroad roadbed rises 100 feet per mile of track. What is the percentage grade for this section of track?
\newline 33. Prove analytically that the diagonals of a square intersect at right angles.
\newline 34. Prove analytically that one median of an isoceles triangle in an altitude.
\newline 35. Prove analytically that the diagonals of a rhombus intersect at right angles.
\\
\newline \textbf{C}
\newline 36. Prove analytically that the medians of an equilateral triangle are altitudes.
\end{document}