\documentclass[10pt,letterpaper]{article}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\begin{document}

\textbf{Analytic Geometry, Third Edition}\\

\textbf{Section 1.7 - Graphs and Points of Intersection}

\textbf{Problems}

\textbf{A} \textit{Plot the graphs of the equations in Problems 1-12. Indicate which give y as a function of x.}

1. $y=2x-1$

2. $x+2y=3$

3. $3x-5y=2$

4. $4x+2y=3$

5. $y=x^2+1$

6. $y=2x-x^2$

7. $y=x^2-x-2$

8. $y=x^2-4x +3$

9. $x^2+y^2=1$

10. $x^2+y^2=16$

11. $y=x^3$

12. $y=x^3-2x^2$

\textit{In Problems 13-16, find the points of intersection and sketch the graphs of the equations.}

13. $3x-5y=2$
$4x+2y=1$

14. $2x+y=-1$
$3x+2y=0$

15. $3x+2y=-1$
$x-4y=-12$

16. $3x-2y=10$
$6x+6y=-1$

\textbf{B} \textit{Plot the graphs of the equations in Problems 17-24. Indicate which give y as a function of x.}

17. $x^2-y^2=4$

18. $x^2-y^2=-4$

19. $4x^2+y^2=4$

20. $x^2-4y^2 =4$

21. $y=\frac{x}{x+1}$

22. $y=\frac{x+1}{x}$

23. $y^2=x^3$

24. $sqrt(x)+sqrt(y)=4$

\begin{quote}
\textit{In Problems 25-32, find the points of intersection annd sketch the graphs of the equations.}
\end{quote}

25.$x-y+2=0$
$y=x^2$

26.
$x- 2y=-1$
$y^2=x+ 4$

27.
$x+ y=1$
$x^2+y^2=5$

28.
$2x+ y=1$
$x^2+y^2=2$

29.
$y=x^2$
$x= y^2$

30.
$y=x^2$
$x^2+y^2=2$

31.
$x+ 2y=3$
$x^2+y^2=4$

32.
$2x+3y=6$
$x^2+y^2=16$

\begin{quote}
\textbf{C}
\end{quote}

33. Plot the graph of $x^2+y^2=0$

34. Plot the graph of $x^2+y^2=-1$

35. Graph $y=x$, $y=x^3$, $y=x^5$, using the same axes. What do you think the graph of $y= x^{99}$ looks like?
\begin{quote}
Verify by plotting a few points with the aid of a pocket calculator. 
\end{quote}

36. Graph $y=x^2$, $y=x^4$, $y=x^6$, using the same axes. What do you think the graph of $y=x^{100}$ looks like?
\begin{quote}
Verify by plotting a few points with the aid of a pocket calculator. 
\end{quote}

37. Graph $y=x$, $y=-x$, $y=|x|$, and $y=\sqrt{x^2}$, noting the similarities and differences. Recall that the definition of $|x|$ is given by
$ |x|=< x if x >= 0, <-x if x < 0$
\begin{quote}
Also note that, while there are normally two square roots of a number, the symbol $\sqrt{}$ is used to represent the nonnegative square root.
\end{quote}

38. Find the points of intersection and sketch the graphs of
a) $x^2+y^2 =4$
    $(x-2)^2+y^2=4$

b) $y=\sqrt{4-(x-2)^2}$
    $x=\sqrt{4-y^2}$

    \begin{quote}
    Note the similarities and differences
    \end{quote}

\end{document}