\documentclass[10pt,letterpaper]{article}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\begin{document}
\textbf{Analytic Geometry, Third Edition}

\textbf{Section 1.8 - An Equation of a Locus}

\medskip
\textbf{Problems}
\medskip

\medskip
\textit{Find an equation for the set of all points (x,y) satisfying the given conditions.}
\medskip

\medskip
\textbf{A}
\medskip

1. It is equidistant from $(5,8)$ and $(-2,4).$

2. It is equidistant from $(2,3)$ and $(-4,1).$

3. Its distance from $(5,8)$ is 3

4. Its distance from $(3,1)$ is 4

\medskip
\textbf{B}
\medskip

5. It is on the line having slope 2 and containing the point $(3,-2)$

6. It is on the line having slope -1 and containing the point $(-2,5)$

7. It is on the line containing $(3,-2)$ and $(5,3)$

8. It is on the line containing $(4,2)$ and $(2,-1)$

9. Its distance from $(0,0)$ is three times its distance from $(4,0)$

10. Its distance from $(2,5)$ is twice its distance from $(-3,1)$

11. It is the vertex of a right triangle with hypotenuse the segment from $(2,5)$ to $(-1,4)$

12. It is the vertex of a right triangle with hypotenuse the segment from $(3,-2)$ to $(1,4)$

13. It is equidistant from $(4,0)$ and the $y\, axis$

14. It is equidistant from $(2,3)$ and the $x\, axis$

15. It is twice as far from $(3,0)$ as it is from the $y\, axis$

16. It is twice as far from $y\, axis$ as it is from $(3,0)$

17. The sum of its distances from $(0,4)$ and $(0,-4)$ is 10

18. The sum of its distances from $(4,-2)$ and $(2,5)$ is 10

19. The sum of the squares of its distances from $(3,0)$ and $(-3,0)$ is 50.

20. The sum of the squares of its distances from $(4,-2)$ and $(2,5)$ is 20.

21. The difference of its distances from $(3,0)$ and $(-3,0)$ is 2

22. The difference of its distances from $(4,2)$ and $(1,-3)$ is 4

23. The product of its distances from the coordinate axes is 4.

24. The product of its distances from $(4,0)$ and the $y\, axis$ is 4.
\end{document}